---
title: "Exercise lesson 8"
author: "Maarten van Doornik"
date: "19 januari 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r main, echo=FALSE, include=FALSE}
source('main.R')
```

## Plot the relationship between Landsat bands and VCF tree cover

These plots show the correlation between the landsat bands and the VCF tree cover:

```{r alldata, echo=FALSE}
pairs(alldata)
```

The plots show us that especially band 4 has a low correlation with the other bands and with the VCF tree cover. The other bands seem to be highly correlated.

## Linear model

Next, a linear model was generated to predict the VCF tree cover from the different landsat band. Below is a summary of this linear model:

```{r linmod}
summary(linmod)
```

## Pedicted vs observed VCF tree cover

With this linear model, the VCF tree cover was predicted for the whole area and compared tot the observed tree cover. Below is a plot of the comparison of both maps:

```{r VCFrasters, echo=FALSE}
levelplot(VCFrasters, col.regions=rev(terrain.colors(255)))
```

This map shows the difference between the two maps:

```{r diff, echo=FALSE}
plot(diff, main='Difference between predicted and observed tree cover')
```

## RMSE

Then the Root mean Squared Error (RMSE) was calculated for the predicted VCF tree cover:

```{r rmse}
print(rmse)
```

## RMSE for different land cover classes

Finally the RMSE was calculated for the different land cover classes cropland, forest and wetland. 

```{r rmse_head, echo=FALSE}
head(df_rmse_classes)
```

From this it can be concluded that the error is different for different land cover classes. Forest shows a substantially lower error than wetland and cropland is in between. 
